Average solar wind and geomagnetic activity influence on the equatorial plasma mass density at geosynchronous orbit

### 2016-07-07 paper/paper.tex
Adding text for new figures

\begin{document}
\title{Solar wind and geomagnetic activity influence on the equatorial plasma mass density at geosynchronous orbit}
\author{V. Veibell and R.S. Weigel}
\doublespacing
\maketitle

@@

%\setlength{\parskip}{3ex}
%\renewcommand{\labelitemi}{$-$}
%\titlespacing{\section}{0pc}{0.2pc}{-1pc}
%\titlespacing{\subsection}{0pc}{0.1pc}{-1pc}
%\titleformat*{\section}{\normalsize\bfseries}
%\titleformat*{\subsection}{\small\bfseries}

%\twocolumn[
%  \begin{@twocolumnfalse}
%\maketitle
%\hrule
\begin{abstract}
We consider two types of events, identified by decreases in $D_{st}$ below a threshold value and increases in the the equatorial mass density at geosynchronous altitudes, $\rho_{eq}$, above a threshold value on 1-hour and 1-day time scales using the \cite{Takahashi2010} dataset.  From the $D_{st}$ events, we find that there is a weak and small amplitude ($< 10$\%) difference between $\rho_{eq}$ on the day of the event and the days before and after on both daily and hourly timescales.  Although very large geomagnetic storms have been observed to correspond to large increases in $\rho_{eq}$, on average, $\rho_{eq}$ following the onset of a geomagnetic storm does not depend on the storm intensity or the north-south component of the interplanetary magnetic field, $B_z$. From the $\rho_{eq}$ events, we find a weak dependence on $B_{z}$ after the onset of an event, with higher average $B_{z}$ six hours after the event onset corresponding to larger $\rho_{eq}$ events.  In contrast, the average of $B_z$ six hours prior to $\rho_{eq}$ events does not have a statistically significant impact on $\rho_{eq}$ after onset.
\end{abstract}
%\vspace{2em}
%\hrule
%\vspace{2em}
% \end{@twocolumnfalse}
%  ]

@@

The dependence of the plasmapause location on geomagnetic activity was observed as early as \cite{Carpenter1966} and there are well--validated models of the plasmapause boundary as a function of $L$, $MLT$, and geomagnetic activity (\cite{LemaireEarthsPlasmasphere}, \cite{Moldwin2002ModelPlasmapause}, \cite{OBrien2003EmpiricalPlasmapause}).  Models also exist for the plasmasphere density (\cite{Gallagher1988EmpiricalModelPlasmasphere}; \cite{LemaireEarthsPlasmasphere}) with similar parameterization.

The dependence of the plasma density outside of the nominal plasmapause location on geomagnetic and solar wind conditions has not been extensively studied until the past decade (\cite{Takahashi2006}; \cite{Takahashi2010}; \cite{Denton2016}). Earlier works that considered profiles of hydrogen ion density found a significant dependence plasmapause location on geomagnetic activity (\cite{Chappell1970}; \cite{Maynard1977}; \cite{Carpenter1992}), but the relationship between geomagnetic activity and density outside of the plasmapause was not explicitly considered.

\cite{Takahashi2006} estimated magnetospheric mass density using measurements from the CRRES satellite during a 73-day period in 1991 when CRRES was in an elliptical, near equatorial orbit and primarily beyond the plasmapause. They found that the local average ion mass, $M$, had some correlation with geomagnetic activity, with more negative hourly $D_{st}$ values corresponding to higher $M$ and 1.5- and 3-day averages of $K_p$ corresponding to higher $M$ (3-hour averages of $K_p$ had little visual correlation with $M$). The mass density estimates were obtained from CRRES observations in the MLT range of [12:00, 18:00] with most observations at $L$ between 5 and 7 $R_E$.

\cite{Denton2006} found a weak relationship between $D_{st}$ and and $K_p$ and the field line distribution of mass density, $\rho$, using observations of the first three toroidal Alfv\'en harmonic frequencies for $L$ in the range of 6-8~$R_E$.  A more pronounced peak in the distribution along a field line near the equator was found for lower $D_{st}$ and larger $K_p$.  The equatorial value of $\rho$ were found to be similar for $D_{st}$ bins of [-142, -31] and [-31, 37] nT and $K_p$ bins of [1.5,3.4] and [3.4, 5.9].

@@

\cite{Takahashi2010} noted that downward spikes in the $D_{st}$ index coincided with with significant changes in $\rho_{eq}$ for $L$ near 6.8~$R_E$. For five storms, two had $\rho_{eq}$ spikes after $D_{st}$ minimum, two had $\rho_{eq}$ spikes before the drop, and one showed little change in $\rho_{eq}$.  A key result was that when daily-averaged measurements were considered, the epoch average of $D_{st}$ exhibited for storms with a minimum $D_{st} < -50$~nT showed an enhancement in $\rho_{eq}$ the same day as minimum $D_{st}$ in the epoch averages.

@@

The above results indicate that (1) the mass density in the at geosynchronous distances is best correlated with $F10.7$ and (2) there exists a much weaker statistical relationship between mass density and the geomagnetic activity indices $K_p$ and $D_{st}$.  In this work we consider the dependence of mass density estimates in the \cite{Takahashi2010} data set and attempt to identify and statistically characterize the relationship between geomagnetic activity with mass density at geosynchronous distances.  In addition, we attempt to identify solar wind processes that may drive changes in mass density.

@@

The parameters $\rho_{eq}$ and $F_{10.7}$ are from the dataset of \cite{Takahashi2010}; data are available from 1980 through 1991 from GOES 2, 3, 5, 6 and 7.  All other parameters used are from \cite{Kondrashov2014ReconstructionOfGaps} which has coverage from 1972 through 2013, which are on a 1--hour time grid. $\rho_{eq}$ is the inferred equatorial mass density based on the 3rd harmonic torodial frequency of magnetic field measurements as described in \cite{Takahashi2010}.  The smallest cadence for $\rho_{eq}$ values is 10 minutes.  To compute an hourly median over the same interval for which the solar wind parameters were averaged, the median of all $\rho_{eq}$ values in a given hour window was used. GOES 6 had the longest span of available data and the primary results presented are for GOES 6 while measurements from other satellites were used for consistency checks.

@@

Figure~\ref{ccplot} shows the long-term trends of log$_{10}(\rho_{eq})$ from GOES 6 and $F_{10.7}$ computed using the median values in 27-day non-overlapping windows.  A scatter plot of these two lines is shown in the lower panel of Figure~\ref{ccplot} along with that for 1--day and 1--hour medians.  The linear correlation for GOES 6 using all measurements is found to be $0.94$, which is the same value documented by \cite{Takahashi2010} who used combined measurements from all satellites in the time interval of 1980 through 1991 using the constraint $0600 \leq MLT \le 1200$, $K_{p3d}\ge1.0$ and $D_{st}\ge -50$~nT.  Our 27-day correlations for GOES 2, 5, and 7 are 0.81, 0.78, and 0.87, and the time range of coverage of measurements from these satellites is 1980-01-01/1983-05-16, 1983-01-01/1987-02-28, and 1983-05-27/1991-08-29, respectively.

@@

The second type of event is an increase in $\rho_{eq}$ above a threshold of 20~amu/cm$^3$.  It is expected that these increases will typically occur after period of quiet geomagnetic activity but may also be the result of increases in geomagnetic activity. In this case, the plasmapause boundary may move outward past geosynchronous orbit and the increase will be due to measurements being made inside the plasmapause.  A second possible reason for the increase could be due to magnetospheric processes.

@@

Our first analysis uses GOES-6 data only from the time interval 1989-1991, which corresponds with the interval used in \cite{Takahashi2010}. In this interval, there were 329 $D_{st}$ events.  For both types of events, the hour of the threshold crossing defines the zero epoch time, and for each event, $4\cdot24$ hours were considered before and $8\cdot24$ hours after event onset.  To compute the epoch averages on a daily time scale, the median value of all available measurements for all events centered on a window of $\pm 12$ hours of the epoch zero hour was computed, and these averaging windows were shifted in increments of $24$~hours. Similar results are obtained if we first reduce each event time series to have a 1-day cadence by computing medians for each event in 1-day bins and then compute the medians across events in each epoch day.

@@

These tests indicate that there is not a statistically significant difference in medians of $\rho_{eq}$ on the day before and day after a threshold crossing in $D_{st}$.  In addition, the observed differences are on the order of only 10\% of the local average of $\rho_{eq}$, which is small compared to the variance in the observations.

@@

The bottom panel of Figure~\ref{HourlyAveragedDstEvents} contains the events shown in the top panel under the constraint that $D_{st}$ remained below -50~nT for at least twelve hours after the event onset time.  In the time period of elevated mass density within 12 hours of the start of the event, there are only $\sim$4 samples per hourly interval.  This result is consistent with previous observations of large mass density spikes in the plasma trough region during large geomagnetic storms (\cite{Yao2008}; \cite{Takahashi2010}).

To determine of this relationship can be also observed in the events of the top panel of Figure~\ref{HourlyAveragedDstEvents}, we sorted the events by the average $D_{st}$ values in the time interval of 0-12 hours, split the events in two and recomputed the epoch averages of $\rho_{eq}$.  The result is that there is no statistically significant difference in the mass density epoch averages for large versus small events.  This indicates that to confirm a statistical $\rho_{eq}$ dependence on large geomagnetic storms would require a dataset with a much larger number of strong geomagnetic storms.

@@

To determine if there is an IMF $B_{z}$ dependence, the epoch curve for $\rho_{eq}$ and $B_{z}$ was separated into two parts depending whether $B_z$ was above or below the average four hours before and including the onset hour and four hours after and including the hour of onset; the result is shown in Figure~\ref{fig:BzBinned}. Any statistically significant difference at a 95\% confidence level between the two parts is indicated by a green dot on the horizontal axis using the same bootstrap method described previously.  (At this confidence level, false positives are expected to randomly occur 5\% of the time or 3.6 times for 72 values.) The largest separation occurs when the separation is performed by Figure~\ref{fig:BzBinned} after onset, with more positive $B_z$ leading to larger peak $\rho_{eq}$ than more negative $B_{z}$.  The rate of change of $\rho_{eq}$ also appears to be insenstive to $B_z$ for approximately 12 hours prior to onset.  We note that the equivalent epoch separation curves for $P_{dyn}$ had a statistically significant differences similar to that for $B_z$, with higher dynamic pressure playing a role similar to positive $B_z$.

@@

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.45]{figures/alldata-GOES6-1983-1991.eps}
\caption{Overview of data used in this article. The top four panels show parameters from \cite{Kondrashov2014ReconstructionOfGaps} and the bottom panel contains $\rho_{eq}$ based on GOES 6 measurements from \cite{Denton} after interpolation and averaging described in the text. Dashed horizontal lines in the $D_{st}$ and $\rho_{eq}$ panels indicate sample event cutoff thresholds of $D_{st} = -50$~nT and $\rho_{eq} = 20$~amu/cm$^3$ considered in Section~3}.
\label{AllData}
\end{figure}

@@

\begin{figure}[tp!]
\centering
\includegraphics[scale=0.40]{figures/stormavs-dst-GOES6.eps}
\\
\rule[1ex]{5cm}{1pt}
\\
\includegraphics[scale=0.40]{figures/stormavs-dd12-GOES6.eps}
\caption{$D_{st}$ events from GOES 6 using hourly medians. Top: Events in the interval 1983-1991; compare to bottom panel Figure~\ref{DailyAveragedDstEvents}. Bottom: Same as Top except for constraint that $D_{st}$ stayed below $-50$~nT for at least 12~hours after crossing below $-50$~nT.}
\label{HourlyAveragedDstEvents}
\end{figure}

@@

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.40]{figures/stormavs-mass-gt20-GOES6.eps}
\caption{$\rho_{eq} >$ 20~amu/cm$^3$ events from GOES 6 using hourly medians. As described in the text, there is no statistically significant dependence of the $\rho_{eq}$  plot on $B_z$ in the time interval of $pm 2$~hours around the event.}
\label{HourlyAveragedRhoEvents}
\end{figure}

>>>>

\begin{document}
\title{Average solar wind and geomagnetic activity influence on the equatorial plasma mass density at geosynchronous orbit}
\author{V. Veibell and R.S. Weigel}
\doublespacing
\maketitle

@@

%\setlength{\parskip}{3ex}

%\titlespacing{\section}{0pc}{0.2pc}{-1pc}
%\titlespacing{\subsection}{0pc}{0.1pc}{-1pc}
%\titleformat*{\section}{\normalsize\bfseries}
%\titleformat*{\subsection}{\small\bfseries}

%\twocolumn[
%  \begin{@twocolumnfalse}
%\maketitle
%\hrule
\begin{abstract}
We consider two types of events, identified by decreases in $D_{st}$ below a threshold value and increases in the the equatorial mass density at geosynchronous altitudes, $\rho_{eq}$, above a threshold value on 1-hour and 1-day time scales using the \cite{Takahashi2010} dataset.  From the $D_{st}$ events, we find that there is a weak and small amplitude ($< 10$\%) difference between $\rho_{eq}$ on the day of the event and the days before and after on both daily and hourly timescales.  Although very large geomagnetic storms have been observed to correspond to large increases in $\rho_{eq}$, on average, $\rho_{eq}$ following the onset of a geomagnetic storm does not depend on the north-south component of the interplanetary magnetic field, $B_z$ near onset time. From the $\rho_{eq}$ events, we find a weak dependence on $B_{z}$ after the onset of an event, with higher average $B_{z}$ four hours after the event onset corresponding to larger $\rho_{eq}$ events.  In contrast, the average of $B_z$ four hours prior to $\rho_{eq}$ events does not have a statistically significant impact on $\rho_{eq}$ after onset.
\end{abstract}
%\vspace{2em}
%\hrule
%\vspace{2em}
% \end{@twocolumnfalse}
%  ]

@@

The dependence of the plasmapause location on geomagnetic activity was observed as early as \cite{Carpenter1966} and there are well--validated models of the plasmapause location as a function of $L$, $MLT$, and geomagnetic activity (\cite{LemaireEarthsPlasmasphere}, \cite{Moldwin2002ModelPlasmapause}, \cite{OBrien2003EmpiricalPlasmapause}).  Models also exist for the plasmasphere density (\cite{Gallagher1988EmpiricalModelPlasmasphere}; \cite{LemaireEarthsPlasmasphere}) with similar parameterization.

The dependence of the plasma density outside of the nominal plasmapause location on geomagnetic and solar wind conditions has not been extensively studied until the past decade (\cite{Takahashi2006}; \cite{Takahashi2010}; \cite{Denton2016}). Earlier works that considered profiles of ion density found a significant dependence of the plasmapause location on geomagnetic activity (\cite{Chappell1970}; \cite{Maynard1977}; \cite{Carpenter1992}), but the relationship between geomagnetic activity and density outside of the plasmapause was not explicitly considered.

\cite{Takahashi2006} estimated magnetospheric mass density using measurements from the CRRES satellite during a 73-day period in 1991 when CRRES was in an elliptical, near equatorial orbit and primarily beyond the nominal plasmapause. They found that the local average ion mass, $M$, had some correlation with geomagnetic activity, with more negative hourly $D_{st}$ values corresponding to higher $M$ and 1.5- and 3-day averages of $K_p$ corresponding to higher $M$ (3-hour averages of $K_p$ had little visual correlation with $M$). The mass density estimates were obtained from CRRES observations in the MLT range of [12:00, 18:00] with most observations at $L$ between 5 and 7 $R_E$.

\cite{Denton2006} found a weak relationship between $D_{st}$ and and $K_p$ and the field line distribution of plasma mass density, $\rho$, using observations of the first three toroidal Alfv\'en harmonic frequencies for $L$ in the range of 6-8~$R_E$.  A more pronounced peak in the distribution along a field line near the equator was found for lower $D_{st}$ and larger $K_p$, but the equatorial value of $\rho$ was found to be similar for $D_{st}$ bins of [-142, -31] and [-31, 37] nT and $K_p$ bins of [1.5,3.4] and [3.4, 5.9].

@@

\cite{Takahashi2010} noted that downward drops in the $D_{st}$ index coincided with significant changes in $\rho_{eq}$ for $L$ near 6.8~$R_E$. For five storms, two had $\rho_{eq}$ spikes after $D_{st}$ minimum, two had $\rho_{eq}$ spikes before the drop, and one showed little change in $\rho_{eq}$.  A key result was that when daily-averaged measurements were considered, the epoch average of $D_{st}$ exhibited for storms with a minimum $D_{st} < -50$~nT showed an enhancement in $\rho_{eq}$ the same day as minimum $D_{st}$ in the epoch averages.

@@

The above results indicate that (1) the mass density in the at geosynchronous distances is best correlated with $F10.7$ and (2) there exists a much weaker statistical relationship between mass density and the geomagnetic activity indices $K_p$ and $D_{st}$.  In this work we consider the dependence of mass density estimates in the \cite{Takahashi2010} data set and attempt to identify and statistically characterize the relationship between geomagnetic activity with mass density at geosynchronous distances.  In addition, we attempt to identify solar wind processes that may drive the changes.

@@

The parameters $\rho_{eq}$ and $F_{10.7}$ are from the dataset of \cite{Takahashi2010}; data are available from 1980 through 1991 from GOES 2, 3, 5, 6 and 7.  All other parameters used are from \cite{Kondrashov2014ReconstructionOfGaps}, which has coverage from 1972 through 2013 and are on a 1--hour time grid. $\rho_{eq}$ is the inferred equatorial mass density based on the 3rd harmonic torodial frequency of magnetic field measurements as described in \cite{Takahashi2010}.  The smallest cadence for $\rho_{eq}$ values is 10 minutes.  To compute an hourly median over the same interval for which the solar wind parameters were averaged, the median of all $\rho_{eq}$ values in a given hour window was used. GOES 6 had the longest span of available data and the primary results presented are for GOES 6 while measurements from other satellites were used for consistency checks.

@@

The top panel of Figure~\ref{ccplot} shows the long-term trends of log$_{10}(\rho_{eq})$ from GOES 6 and $F_{10.7}$ computed using the median values in 27-day non-overlapping windows.  A scatter plot of these two lines is shown in the lower panel of Figure~\ref{ccplot} along with that for 1--day and 1--hour medians.  The linear correlation for GOES 6 using all measurements is found to be $0.94$, which is the same value documented by \cite{Takahashi2010} who used combined measurements from all satellites in the time interval of 1980 through 1991 using the constraint $0600 \leq MLT \le 1200$, $K_{p3d}\ge1.0$ and $D_{st}\ge -50$~nT.  Our 27-day correlations for GOES 2, 5, and 7 are 0.81, 0.78, and 0.87, and the time range of coverage of measurements from these satellites is 1980-01-01/1983-05-16, 1983-01-01/1987-02-28, and 1983-05-27/1991-08-29, respectively.

@@

The second type of event is an increase in $\rho_{eq}$ above a threshold of 20~amu/cm$^3$.  It is expected that these increases will typically occur after period of quiet geomagnetic activity but may also be the result of increases in solar wind driven geomagnetic activity. In this case, the plasmapause boundary may move outward past geosynchronous orbit and the increase will be due to measurements being made inside the plasmapause.  A second possible reason for the increase could be due to magnetospheric processes.

@@

Our first analysis uses GOES-6 data only from the time interval 1989-1991, which corresponds with the interval used in the epoch analysis of \cite{Takahashi2010}. In this interval, there were 329 $D_{st}$ events.  For both types of events, the hour of the threshold crossing defines the zero epoch time, and for each event, $4\cdot24$ hours were considered before and $8\cdot24$ hours after event onset.  To compute the epoch averages on a daily time scale, the median value of all available measurements for all events centered on a window of $\pm 12$ hours of the epoch zero hour was computed, and these averaging windows were shifted in increments of $24$~hours. Similar results are obtained if we first reduce each event time series to have a 1-day cadence by computing medians for each event in 1-day bins and then compute the medians across events on each epoch day.

@@

These tests indicate that there is not a statistically significant difference in medians of $\rho_{eq}$ on the day before and day after a threshold crossing in $D_{st}$.  In addition, the observed differences are on the order of only 10\% of the value of $\rho_{eq}$ on the onset day, which is similar to the variation in the observations over the displayed epoch time interval.

@@

The bottom panel of Figure~\ref{HourlyAveragedDstEvents} contains the events shown in the top panel under the constraint that $D_{st}$ remained below -50~nT for at least twelve hours after the event onset time.  In the time period of elevated mass density within 12 hours of the start of the event, there are only $\sim$4 samples per hourly interval.  This result is consistent with previous observations of large mass density increases in the plasma trough region during large geomagnetic storms (\cite{Yao2008}; \cite{Takahashi2010}).

The top panel of Figure~\ref{HourlyAveragedDstEvents} shows that, on average, near the onset of $D_{st}$ events there is not a significant reponse in $\rho_{eq}$ while the bottom panel shows that for rare and large $D_{st}$ events elevated $\rho_{eq}$ can be observed.  To determine if there is an IMF $B_{z}$ dependence, the epoch curves in the top panel of Figure~\ref{HourlyAveragedDstEvents} for $\rho_{eq}$ and $B_{z}$ were separated into two parts depending whether $B_z$ was above or below its average four hours before and including the onset hour and four hours after and including the hour of onset; the result is shown in Figure~\ref{fig:BzBinnedDstEvents}. Any statistically significant difference at a 95\% confidence level between the two parts is indicated by a green dot on the horizontal axis using the same bootstrap method described previously.  (At this confidence level, false positives are expected to randomly occur 5\% of the time, or 3.6 times for 72 values.)  These two curves indicate that there is not a statistically significant dependence on IMF $B_{z}$ around the time of the onset of a $D_{st}$ event.

The process for creating Figure~\ref{fig:BzBinnedDstEvents} was repeated except using the sort variable $F10.7$ instead of $B_z$, as shown in Figure~\ref{fig:F107BinnedDstEvents}. As expected, difference between the epoch curves is statistically significant at all times, as expected, but elevated $F10.7$ is associated with a peak in the $\rho_{eq}$ curve approximately 5 hours after onset.

@@

The largest difference occurs when the separation is performed after onset, with more positive $B_z$ leading to larger peak $\rho_{eq}$ than more negative $B_{z}$.  The rate of change of $\rho_{eq}$ also appears to be insenstive to $B_z$ for approximately 12 hours prior to onset.  The equivalent epoch separation curves for $P_{dyn}$ had a statistically significant differences similar to that for $B_z$, with higher dynamic pressure playing a role similar to positive $B_z$.

@@

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.45]{figures/alldata-GOES6-1983-1991.eps}
\caption{Overview of data used in this article. The top four panels show parameters from \cite{Kondrashov2014ReconstructionOfGaps} and the bottom panel contains $\rho_{eq}$ based on GOES 6 measurements from \cite{Denton} after interpolation and averaging described in the text. Dashed horizontal lines in the $D_{st}$ and $\rho_{eq}$ panels indicate sample event cutoff thresholds of $D_{st} = -50$~nT and $\rho_{eq} = 20$~amu/cm$^3$ considered in Section~3.}
\label{AllData}
\end{figure}

@@

\begin{figure}[tp!]
\centering
\includegraphics[scale=0.40]{figures/stormavs-dst-GOES6.eps}
\\
\rule[1ex]{5cm}{1pt}
\\
\includegraphics[scale=0.40]{figures/stormavs-dd12-GOES6.eps}
\caption{$D_{st}$ events from GOES 6 using hourly medians. Top: Events in the interval 1983-1991. Bottom: Same as Top except for constraint that $D_{st}$ stayed below $-50$~nT for at least 12~hours after crossing below $-50$~nT.}
\label{HourlyAveragedDstEvents}
\end{figure}

\clearpage
\begin{figure}[tp!]
  \centering
  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedB_z-case1-t020-tf25-GOES6.eps}
  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedB_z-case1-t025-tf30-GOES6.eps}
  \caption{$D_{st}$ events of Figure~\ref{HourlyAveragedDstEvents} separated by the average $D_{st}$ value (a) at onset and four hours before, and (b) at onset and four hours after.}
  \label{fig:BzBinnedDstEvents}
\end{figure}

\begin{figure}[tp!]
  \centering
  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedF107-case1-t020-tf25-GOES6.eps}
  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedF107-case1-t025-tf30-GOES6.eps}
  \caption{$D_{st}$ events of Figure~\ref{HourlyAveragedDstEvents} separated by the average $F10.7$ value (a) at onset and four hours before, and (b) at onset and four hours after.}
  \label{fig:F107BinnedDstEvents}
\end{figure}

@@

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.40]{figures/stormavs-mass-gt20-GOES6.eps}
\caption{$\rho_{eq} >$ 20~amu/cm$^3$ events from GOES 6 using hourly medians.}
\label{HourlyAveragedRhoEvents}
\end{figure}
